Histograms

### 2022-03-17 analysis/histograms.Rmd
Revert "fix: working directory for targets"
This reverts commit cac14f630848b078c39aee7344862d418fcdcb52.
fix: MELD probailities

---
title: "Histograms"
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

@@

>>>>

---
title: "Histograms"
---

@@

# MELD Scores (imputed)

```{r histograms_meld, results = "asis", message = FALSE, warning = FALSE}
meldv <-
    c(paste0("ScoreMeld", c("", "Unos", "Na", "NaUnos")),
      paste0("SurvProbMeld", c("Unos", "NaUnos", "Plus7")))
for (v in meldv) {
    cat("\n\n##", v , "\n\n")
    .hist(zlog_data[[v]], main = paste0("Histogram of ", v), xlab = v)
    .qqnorm(zlog_data[[v]], yname = v)
}
```
